---
title: 'Graphite storage issues'
date: 'March 17, 2017'
output:
  html_document: default
  html_notebook: default
---

A recent repeat of CLIVAR samples from graphite produced a few Fm values ~30 permil different from the first run, I started looking into sources of contamination. The test below is of four leftover splits of CLIVAR graphite run after being stored for about a month. The first two were stored upside down with graphite in contact with the cap, and the second two were stored upright.

```{r}
suppressMessages(library(amstools))
suppressMessages(library(tidyverse))
library(odbc)
library(knitr)

  query <- "SELECT
              mst_num, wheel, runtime, snics_raw.tp_num, osg_num, sample_name, 
              ok_calc, le12c, he13_12, he14_12
            FROM snics_raw
            JOIN target ON target.tp_num = snics_raw.tp_num
            WHERE osg_num IN (157120, 157119, 157122, 157121)"

  db <- conNOSAMS()
  data <- dbGetQuery(db, query)
  data <- arrange(data, mst_num)
```

Plotting the raw 14/12 ratio shows there's a huge burn-in effect, and that the values stabilize about 10% low.

```{r}
ggplot(data, aes(mst_num, he14_12, color = wheel)) +
  geom_line() + geom_point() + facet_grid(. ~ osg_num) +
  ggtitle("Raw 14/12 measurements")
```

Looking at the normalized data with the "burn in" pruned off, there are still some big differences when the samples are touching the cap.

```{r}
query <- "SELECT
            wheel, runtime, snics_results.tp_num, osg_num, sample_name, 
            del_13c, fm_corr, sig_fm_corr
          FROM snics_results
          JOIN target ON target.tp_num = snics_results.tp_num
          WHERE osg_num IN (157120, 157119, 157122, 157121)"

data <- dbGetQuery(db, query)

options(digits = 3)

data %>% 
  arrange(osg_num) %>% 
  mutate(fm_corr = round(fm_corr, digits = 3), sig_fm_corr = round(sig_fm_corr, digits = 3)) %>%
  select(osg_num, wheel, fm_corr, sig_fm_corr) %>%
  unite(fm_corr, sig_fm_corr, col = "Fm", sep = " +- ") %>%
  spread(wheel, Fm) %>%
  kable()

ggplot(data, aes(osg_num, fm_corr, color = wheel)) +
  geom_pointrange(aes(ymin = fm_corr - sig_fm_corr, ymax = fm_corr + sig_fm_corr)) + 
  geom_point() 

```

