---
title: "Do standards degrade with time?"
author: "Brett Longworth"
date: "March 22, 2017"
output: html_document
---

What effect does the time between graphitization and analysis have on data quality? How long can a pressed sample wait for analysis?

Samples are large (>40umol) secondaries from both systems. I've also discarded samples with wild sigma and those older than 100 days. I can't see an obvious trend in the data, but it's likely that any smaller trends are masked by the distribution in time between graphitization and running.
```{r, warning=FALSE, message=FALSE}
# libraries
library(lubridate)
library(dplyr)
library(ggplot2)
library(knitr)

# data
load('qcData.rda')

# format dates
std$gf_date <- ymd(std$gf_date)
std$tp_date_pressed <- ymd(std$tp_date_pressed)
std$runtime <- as.Date(ymd_hms(std$runtime))
std$tgr <- std$runtime - std$gf_date
std$tpr <- std$runtime - std$tp_date_pressed

# filter it
std.f <- filter(std, tgr < 100,
                tpr < 20, 
                abs(sigma) < 20, 
                normFm < 20,
                primary == FALSE, 
                frep_err < 10, 
                fm_consensus > 0.1, 
                fm_consensus < 1.6, 
                gf_co2_qty > 40) %>%
  mutate(runtime = as.Date(runtime),
         year = year(runtime),
         month = month(runtime)) 
```

## Summary data

Median times are probably more representitive.

```{r, message=FALSE, warning=FALSE}

std.f %>% group_by(system) %>%
  select(system, tgr, tpr) %>%
  summarize(tgr.mean = mean(tgr),
            tgr.median =  median(tgr),
            tgr.sd = sd(tgr),
            tpr.mean = mean(tpr),
            tpr.median = median(tpr),
            tpr.sd = sd(tpr),
            N = n()) %>%
  kable()

bymonth <- std.f %>% group_by(year, month, system) %>%
  summarize(tgr.mean = mean(tgr),
            tgr.median =  median(tgr),
            tgr.sd = sd(tgr),
            tpr.mean = mean(tpr),
            tpr.median = median(tpr),
            tpr.sd = sd(tpr),
            N = n()) %>%
  mutate(date = as.factor(mdy(sprintf('%s %s %s', month, "1", year))))

#kable(bymonth)

ggplot(bymonth, aes(date, tgr.median)) +
  geom_bar(aes(fill = system), stat = "identity", position = "dodge") +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))  +
  ggtitle("Time between graphitization and running over time")

ggplot(bymonth, aes(date, tpr.median)) +
  geom_bar(aes(fill = system), stat = "identity", position = "dodge") +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
  ggtitle("Time between pressing and running over time")

ggplot(std.f, aes(tgr)) +
  geom_histogram() +
  facet_grid(.~system) +
  ggtitle("Distribution of time between graphitization and running")
ggplot(std.f, aes(tpr)) +
  geom_histogram() +
  facet_grid(.~system) +
  ggtitle("Distribution of time between pressing and running")
```

### Plots 

Time between graphitization and being run on the machine.
```{r, message=FALSE}
qplot(tgr, sigma, data = std.f, color = f_modern) +
  geom_smooth() + facet_grid(.~ system) +
  ggtitle("Sigma vs time between graphitization and running")
qplot(tgr, frep_err, data = std.f, color = f_modern) +
  geom_smooth() + facet_grid(.~ system) +
  ggtitle("Reported error vs time between graphitization and running")
```

Time between pressing and running

```{r, warning=FALSE, message=FALSE}
qplot(tpr, sigma, data = std.f, color = f_modern) +
  geom_smooth() +
  facet_grid(.~ system) +
  ggtitle("Sigma vs. time between pressing and running")
qplot(tpr, frep_err, data = std.f, color = f_modern) + geom_smooth() + facet_grid(.~ system) +
  ggtitle("Relative reported error vs. time between pressing and running")
```

