---
title: "Do standards degrade with time?"
author: "Brett Longworth"
date: "March 22, 2017"
output: html_document
---

What effect does the time between graphitization and analysis have on data quality? How long can a pressed sample wait for analysis?

Samples are large (>40umol) secondaries from both systems. I've also discarded samples with wild sigma and those older than 100 days. I can't see an obvious trend in the data, but it's likely that any smaller trends are masked by the distribution in time between graphitization and running.
```{r, warning=FALSE, message=FALSE}
# libraries
library(tidyverse)
library(lubridate)
library(knitr)
library(amstools)
library(amsdata)

# data

std <- getStandards('2014-01-01', getcurrents = FALSE) |> 
  mutate(system = str_sub(wheel, 1, 5),
         sig_f_modern = pmax(f_int_error, f_ext_error),
         sigma = sigma(f_modern, Fm_cons, sig_f_modern),
         tgr = difftime(runtime, gf_date, units = 'days'),
         tpr = difftime(runtime, tp_date_pressed, units = 'days'))

std.f <- std |> 
  filter(tgr < 100,
         tgr > 0,
         tpr < 20, 
         tpr > 0, 
         abs(sigma) < 20, 
         sample_type != "S", 
         Fm_cons > 0.1, 
         Fm_cons < 1.6, 
         gf_co2_qty > 40) %>%
  mutate(runtime = as.Date(runtime),
         year = year(runtime),
         month = month(runtime)) 
```

## Summary data

Median times are probably more representitive.

```{r, message=FALSE, warning=FALSE}

std.f %>% group_by(system) %>%
  select(system, tgr, tpr) %>%
  summarize(tgr.mean = mean(tgr),
            tgr.median =  median(tgr),
            tgr.sd = sd(tgr),
            tpr.mean = mean(tpr),
            tpr.median = median(tpr),
            tpr.sd = sd(tpr),
            N = n()) %>%
  kable()

bymonth <- std.f %>% group_by(year, month, system) %>%
  summarize(tgr.mean = mean(tgr),
            tgr.median =  median(tgr),
            tgr.sd = sd(tgr),
            tpr.mean = mean(tpr),
            tpr.median = median(tpr),
            tpr.sd = sd(tpr),
            N = n()) %>%
  mutate(date = as.factor(mdy(sprintf('%s %s %s', month, "1", year))))

#kable(bymonth)

ggplot(bymonth, aes(date, tgr.median)) +
  geom_bar(aes(fill = system), stat = "identity", position = "dodge") +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))  +
  ggtitle("Time between graphitization and running over time")

ggplot(bymonth, aes(date, tpr.median)) +
  geom_bar(aes(fill = system), stat = "identity", position = "dodge") +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
  ggtitle("Time between pressing and running over time")

ggplot(std.f, aes(tgr)) +
  geom_histogram() +
  facet_grid(.~system) +
  ggtitle("Distribution of time between graphitization and running")
ggplot(std.f, aes(tpr)) +
  geom_histogram() +
  facet_grid(.~system) +
  ggtitle("Distribution of time between pressing and running")
```

### Plots 

Time between graphitization and being run on the machine.
```{r, message=FALSE}
qplot(tgr, sigma, data = std.f, color = f_modern) +
  geom_smooth() + facet_grid(.~ system) +
  ggtitle("Sigma vs time between graphitization and running")
qplot(tgr, abs(sigma), data = std.f, color = f_modern) +
  geom_smooth() + facet_grid(.~ system) +
  ggtitle("Absolute Sigma vs time between graphitization and running")
# qplot(tgr, frep_err, data = std.f, color = f_modern) +
#   geom_smooth() + facet_grid(.~ system) +
#   ggtitle("Reported error vs time between graphitization and running")
```

Time between pressing and running

```{r, warning=FALSE, message=FALSE}
qplot(tpr, sigma, data = std.f, color = f_modern) +
  geom_smooth() +
  facet_grid(.~ system) +
  ggtitle("Sigma vs. time between pressing and running")
# qplot(tpr, frep_err, data = std.f, color = f_modern) + geom_smooth() + facet_grid(.~ system) +
#   ggtitle("Relative reported error vs. time between pressing and running")
```

