---
title: "Pressed Target Storage"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

Results of pressed target storage tests on CFAMS and USAMS. Blank material was left under various conditions to determine which is best for pressed target storage.


```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(odbc)

theme_set(theme_classic())

# Define plot
plot_storage <- function(df, c_avg, c_sd, p_avg, p_sd) {
  ggplot(df, aes(treatment, norm_ratio, color = type)) +
    geom_hline(yintercept = p_avg, color = 'grey') +
    geom_hline(yintercept = p_avg + p_sd, color = '#00b7bd') +
    geom_hline(yintercept = p_avg - p_sd, color = '#00b7bd') +
    geom_hline(yintercept = c_avg, color = 'grey') +
    geom_hline(yintercept = c_avg + c_sd, color = '#b7bf10') +
    geom_hline(yintercept = c_avg - c_sd, color = '#b7bf10') +
    geom_pointrange(aes(ymin = norm_ratio - max_err, ymax = norm_ratio + max_err), 
                    position = position_jitter(width = 0.1, height = 0)) +
    scale_color_manual(values = c("#00b7bd", "#b7bf10")) +
    ylim(0, 0.005) +
    theme_classic()
}

# Get data
con <- amstools::conNOSAMS()
query <- "SELECT wheel, wheel_pos, runtime, sample_name, num_runs, 
            tot_runs, norm_ratio, int_err, ext_err
          FROM snics_results
          WHERE (wheel = 'CFAMS100218' AND wheel_pos > 113)
          OR wheel = 'USAMS112818' AND wheel_pos > 86"
data <- dbGetQuery(con, query) |> 
  mutate(max_err = pmax(int_err, ext_err), 
         type = case_when(grepl("C-1", sample_name) ~ "C-1",
                          grepl("TIRI", sample_name) ~ "TIRI-F",
                          TRUE ~ "Ceylon"),
         type = ordered(type, c("C-1", "TIRI-F", "Ceylon")),
         treatment = c(rep(c("Air", "Dry Box", "Oven", "Vac Oven", "Vac Bag"), 2),
         c("Oven", "Dry Box", "Vac Bag", "Air", "Vac Oven", "Control", "Air", 
           "Air", "Air", "Dry Box", "Dry Box", "Dry Box", "Oven", "Oven", 
           "Oven", "Vac Oven", "Vac Oven", "Vac Oven", "Control", "Control")))
```


# CFAMS

Large Tiri-F samples were combined and then split into 10 targets. These and 5 Ceylon graphite targets were stored for two weeks before being analysed. 2 Tiri-F and one Ceylon were stored under the following conditions: in air on top of the drybox, in the drybox, sealed in a food saver vacuum bag on top of the vacuum oven, in the drying oven at 70C, and in a vacuum oven at approx. 60C.

```{r}
data |> 
  filter(wheel == 'CFAMS100218') |> 
  plot_storage(0.0009, 0.0006, 0.0022, 0.001)
```

Plot shows the normalized ratios (not blank corrected) of the C-1 and Ceylon samples from the test. Control treatment is fresh C-1 and Ceylon pressed for the wheel. Error bars are the maximum of the internal and external errors. The blue lines are the 2018 sd for C-1, yellow lines are sd for Ceylon, and the grey lines are the averages of 2018 measurements for each material. 

For Tiri-F, Air, Drybox and Oven treatments are pretty much the same while the vacuum bag and vacuum oven may be worse. For ceylon, Air, Drybox and Vac oven were all the same, while the oven and Vac bag were slightly better. Error bars are overlapping or close to overlapping for most points.

# USAMS

The USAMS experiment was done similarly to the CFAMS experiment. Pooled C-1 was used instead of TIRI-F, and the vacuum bag test was dropped. Samples were stored for about two weeks.

```{r}
data |> 
  filter(wheel == 'USAMS112818') |> 
  plot_storage(0.0004, 0.0001, 0.0009, 0.0003)
```

Plot shows the normalized ratios (not blank corrected) of the C-1 and Ceylon samples from the test. Control treatment is fresh C-1 and Ceylon pressed for the wheel. Error bars are the maximum of the internal and external errors. The blue lines are the 2018 sd for C-1, yellow lines are sd for Ceylon, and the grey lines are the averages of 2018 measurements for each material. 

# Summary

For C-1, Air, Drybox and Oven treatments are pretty much the same while the vacuum oven may be worse. For ceylon, Air, oven and Vac oven were all the same, while the oven was slightly worse. Error bars are overlapping or close to overlapping for most points. Most storage results were not significantly worse than fresh samples or historical values.